%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {Production Engineer} % Job title
    {Optiver} % Organization
    {Amsterdam, The Netherlands} % Location
    {Aug. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Responsible for deploying, maintaining, monitoring and improving the reliability, scalability and performance of Optiver's in-house built trading systems and infrastructure.}
      \item {Prevention \& swift resolution of incidents across the technology stack, to guarantee optimum availability even in the most extreme market conditions. }
       \item {Eliminating toil and seeking operational efficienices with Python, Ansible, and custom reporting.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Site Reliability Engineer - Tech Lead} % Job title
    {Commonwealth Bank of Australia} % Organization
    {Sydney, Australia} % Location
    {Oct. 2022 - Aug. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Spearheaded development of new Grafana/Mimir/Prometheus observability stack, ensuring compliance with APRA regulations and ISO 27001}
      \item {Reduced toil and optimized efficiency through custom Go tooling and troubleshooting complex issues in EKS Kubernetes environments}
      \item {Implemented CI/CD pipelines using Jenkins and Octopus Deploy, reducing lead time to change from weeks to minutes}
      \item {Led and mentored a high-performing SRE team of 20+ engineers, establishing best practice and a solid engineering foundation}
      \item {Delivered strategic presentations to audiences of 100-1,000+ staff, including senior leadership and C-level executives}
      \item {Spearheaded the Master Service Agreement (MSA) and procurement of PagerDuty, resulting in the largest PagerDuty installation in APAC at the time, a deal worth \$x million over 3 years}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Site Reliability Engineer - Team Lead} % Job title
    {Teleport} % Organization
    {Sydney, Australia} % Location
    {Sep. 2021 - Jul. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Incident management, co-ordination and resolution of operational issues across Kubernetes, and AWS (S3, DynamoDB, IAM)}
        \item {Architecture and design of storage and authentication components in a bespoke Kubernetes operator written in Go to support multi-tenancy}
        \item {Hiring (interviews, designing the hiring challenge), coaching and staff on professional development}
        \item {Various DevRel contributions: Conference talks, booth attendance, demo videos }
        \item {Monitoring, alerting and dashboarding through Grafana, Prometheus, PagerDuty}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {System Development Engineer} % Job title
    {Google} % Organization
    {Sydney, Australia} % Location
    {Jul. 2018 - Aug. 2021} % Date(s)
    {
    \begin{cvitems}
      \item {Maintained a globally distributed CDN (Google Global Cache) spanning 1,300+ cities in 200+ countries, supporting products like YouTube}
      \item {Developed an on-device Go-based monitoring solution for top-of-rack switches, communicating health status via serial output}
      \item {Implemented bug fixes and features for the public-facing \href{https://peering.google.com/}{Google ISP Portal} using Python, JavaScript, and SASS}
      \item {Created a Go-based rules-driven ingestion engine for routing, prioritizing, and auto-remediating inbound tickets based on text configurations}
      \item {Managed fleet reporting and metrics (SQL, Dashboarding) to ensure high cache efficiency, such as monitoring annualized HDD failure rates using Python}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Systems Development Engineer} % Job title
    {Amazon Web Services} % Organization
    {Sydney, Australia} % Location
    {Apr. 2015 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scaling, monitoring and fire-fighting the Amazon RDS control plane powering the largest database fleet in the world}
        \item {Designed and built a solution in Java to ingest and analyse alarming data to identify operational trends and patterns }
        \item {Built supporting tools, including a web application in Python to understand and interpret ingested data both in real time\\
        and in automated weekly reports to stakeholders (to the GM level)}
        \item {Documented \& drove process change that uses this data to influence the cadence and velocity of feature development }
        \item {Participate in hiring (100+ interviews) identifying potential in candidates to help fuel Amazon's expansive growth}
      \end{cvitems}
    }
\end{cventries}
